Methods for Analyzing Models of Rod-Shaped Bacteria

### 2025-07-07 paper/main.tex
split into two separate figures

%###################################################################################################
\section{Parameter Estimation}
\label{sec:supplement-parameter-profiles}
%TODO {explain profiles}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-0.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-1.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-2.pdf}\\%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-3.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-4.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-5.pdf}\\%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/radius-0.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/radius-1.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/radius-2.pdf}\\%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/radius-3.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/radius-4.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/radius-5.pdf}%
        \caption{}%TODO insert caption}
    \label{fig:parameter-estimates-supplement}
\end{figure}

>>>>

%###################################################################################################
\section{Parameter Estimation}
\label{sec:supplement-parameter-profiles}
%TODO {explain profiles}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-0.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-1.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-2.pdf}\\%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-3.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-4.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-5.pdf}
    \caption{Parameter estimation of growth rates for individual cells}%TODO extend caption}
    \label{fig:parameter-estimates-supplement}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/radius-0.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/radius-1.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/radius-2.pdf}\\%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/radius-3.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/radius-4.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/radius-5.pdf}%
    \caption{Parameter estimation of radii for individual cells}%TODO extend caption}
    \label{fig:parameter-estimates-supplement}
\end{figure}
